---
title: "Dataset"
author: "Akshat Dwivedi"
date: "17 April 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache = TRUE, fig.width = 11)
```

# Tumor Marker Data

Taken from [here](https://labs.genetics.ucla.edu/horvath/kidneypaper/RCC.htm).

```{r}
library(dplyr)
library(ggplot2)
library(readr)

m = read_csv("/home/ad/Desktop/KUL Course Material/Robust Statistics/Project/Data/TutorialRCC366/testData_366.csv") %>% dplyr::select(-`NA`) %>% mutate(ClearCell = as.factor(ClearCell), event = as.factor(event))

glimpse(m)
```

```{r}
table(m$ClearCell) # G = 2, p = 8 (8 markers)
```

Two Groups: Clear and non-clear cell. So G = 2, p = 8 (8 different markers). In the example in the paper they've got (Banknote data from UCI as well, same as the tumor marker data) they have G = 2 and p = 4.

```{r}
pairs(formula = ~., data = m[,1:8], col = m$ClearCell)
```

Shows the plots for different marker values for different groups.

# Motorins Data (package: faraway)

```{r}
library(faraway)
data("motorins")

str(motorins)
```

Shows the vairables in the dataset.

```{r}
pairs(formula = ~., data = motorins[,5:7], col = as.factor(motorins$Bonus), main = "Bonus")
table(motorins$Bonus)
```

Shows skewed variables Insured, Claims and Payment at different levels of categorical var Bonus.

```{r}
pairs(formula = ~., data = motorins[,5:7], col = motorins$Kilometres, main = "Kilometers")
```

Same but with Kilometers.

Could also just collapse the data into smaller groups by considering only two levels of one of the categorical variables instead of considering 5 or 7 levels.

```{r}
pairs(formula = ~., data = motorins[,5:7], col = motorins$Zone, main = "Zone")
```

```{r}
pairs(formula = ~., data = motorins[,5:7], col = motorins$Make, main = "Make")
```

### Variable Description

```
A data frame with 1797 observations on the following 8 variables.

Kilometres
an ordered factor representing kilomoters per year with levels 1: < 1000, 2: 1000-15000, 3: 15000-20000, 4: 20000-25000, 5: > 25000

Zone
a factor representing geographical area with levels 1: Stockholm, Goteborg, Malmo with surroundings 2: Other large cities with surroundings 3: Smaller cities with surroundings in southern Sweden 4: Rural areas in southern Sweden 5: Smaller cities with surroundings in northern Sweden 6: Rural areas in northern Sweden 7: Gotland

Bonus
No claims bonus. Equal to the number of years, plus one, since last claim

Make
A factor representing eight different common car models. All other models are combined in class 9

Insured
Number of insured in policy-years

Claims
Number of claims

Payment
Total value of payments in Skr

perd
payment per claim
```
